---
title: "R-Practice"
author: | 
  | Abhishek Bhatia
  | PGDSMA ISI TEZPUR 2019/20
  | R: Intro to packages
date: "12th September 2019"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

1. Use airquality dataframe to create a data frame which
calculates the monthly average of Ozone, Solar.R, Wind and
Temp.
New dataframe will be of this form <br />
Month Avg. Ozone Avg. Solar.R Avg. Wind Avg. Temp  <br />
May <br />
June <br />
July <br />
August <br />
September <br />
```{r}
# Q1 
df <- airquality
res <- aggregate(subset(df, select=-Day), by=list(df$Month), 
                 FUN = mean, na.rm=T)
# Drop month column
res <- res[, -ncol(res)]

res[, "Group.1"] <- sapply(res[, "Group.1"], FUN = function (m) month.name[m])

# Change column names
colnames(res) <- c("Month", paste0("Avg.", colnames(res)[2:ncol(res)]))

res

```

2. mtcars dataset

i. Give the names of the cars in order of decreasing mpg <br />
ii. find how many different types of cyl is there for cars having <br />
mpg greater than 18
iii. make a bar plot to show how many cars are there with
different cyl above mpg 18 <br />
iv. rank the cars (only names) in decreasing order of wt only till
wt = 3 <br />

```{r}
# Q2
df <- mtcars

# i. Give the names of the cars in order of decreasing mpg
rownames(df[order(df$mpg, decreasing = T), ])
```


```{r}
# ii. find how many different types of cyl is there for cars having
#     mpg greater than 18

length(unique(subset(df, mpg > 18, select = cyl)$cyl))
```


```{r}
# iii. make a bar plot to show how many cars are there with
#      different cyl above mpg 18

# Ref: Stackoverflow: all names in x-axis barplot https://t.ly/dxdWw
df.cyl.gt18 <- subset(df, mpg > 18, select=c(cyl))
t <- table(df.cyl.gt18)
names(dimnames(t)) <- NULL

barplot(t, xlab = "cylinders", ylab = "No. of Cars", 
        main = "Distribution of cars with different number of cylinders")
```


```{r}
# iv. rank the cars (only names) in decreasing order of wt only till
#     wt = 3

row.names(subset(df[order(df$wt, decreasing = T), ], wt >= 3))
```

3. PlantGrowth dataset

```{r}
# Q3
df <- PlantGrowth
df$group <- as.factor(df$group)
cols <- c("red", "green", "blue")[as.factor(df$group)]
plot(df$weight, df$group, col = cols, ylab = "Type", xlab = "")
# NOT WORKING IN R notebook?
legend("topleft", legend = c("Control", "Treatment1", "Treatment2"),
       col = c("red", "green", "blue"),
       pch = 1)
```

4. 
i. Load practice.txt in R into a data frame with two columns as
A and B from the file. < br/>
ii. Compute the mean row wise and add as column < br/>
iii. Compute the mean column wise and add as row < br/>
iv. Save the modified data frame as csv file < br/>

```{r}
# Q4
# i. Load practice.txt in R into a data frame with two columns as
#    A and B from the file.

# Check first 5 lines to find a pattern
# They seem to be : separated
f <- "practice.txt"
for (l in readLines(f, n = 5)){
  cat(l, "\n")
}

df <- read.table(f, sep = ":")
head(df)
```


```{r}
# ii. Compute the mean row wise and add as column
res <- cbind(df, rowMeans(df))
colnames(res)[ncol(res)] <- "rowmean"
```


```{r}
# iii. Compute the mean column wise and add as row
res <- rbind(res, colMeans(res))
rownames(res)[nrow(res)] <- "colmean"
```
This is how our result looks like
```{r}
res
```



```{r}
# iv. Save the modified data frame as csv file
ofile <- "practice_output.txt"
write.csv(res, ofile)
```


